Technical Report

### 2018-04-10 fully-abstract-comp/technical-report.tex
Fix layout.
Modify proposed component relation to require purity of imports and exports.
Another update to the component relation
* Quantify over future worlds in which imports may be valid.
* Fix relation requirements for main capability pair
Define context plugging as component linking + initial execution configuration construction.

@@

\begin{align*}
  \lrcomp(W) =
  \left\{\begin{multlined}
     \npair{\var{comp},\var{comp}} \;\mid \;\\
      \var{comp} = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss) \tand \\
      W \vdash \var{comp} \tand\\
      \forall W' \ldotp \text{If } W \oplus W' \text{ is defined }\\
      \tand \overline{\npair{(c_{\mathrm{import}},c_{\mathrm{import}})}} \in \lrv(W')\\
      \text{then } \overline{\npair{(c_{\mathrm{export}},c_{\mathrm{export}})}} \in \lrv(W)
  \end{multlined}
    \right\} \cup
  \left\{\begin{multlined}
     \npair{(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}),(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})} \;\mid \;\\
     \npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W) \tand
      W \vdash \var{comp} \tand\\
      \forall W' \ldotp \text{If } W \oplus W' \text{ is defined }\\
      \tand \overline{\npair{(c_{\mathrm{import}},c_{\mathrm{import}})}} \in \lrv(W')\\
      \text{then } \overline{\npair{(c_{\mathrm{export}},c_{\mathrm{export}})}} \in \lrv(W)
  \end{multlined}
    \right\} \cup
\end{align*}

>>>>

\begin{definition}[Plugging a program into a context]
  When $\var{comp'}$ is a context for component $\var{comp}$, $\var{comp}' \bowtie \var{comp} \rightsquigarrow \Phi$.
  Then we write $\plug{\var{comp'}}{\var{comp}}$ for the execution configuration $\Phi$.
\end{definition}

@@

\begin{align*}
  \lrcomp(W) &=
  \left\{\begin{multlined}
     \npair{\var{comp},\var{comp}} \;\mid \;\\
      \var{comp} = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss) \tand \\
      W \vdash \var{comp} \tand\\
      \text{For all } W' \future W \ldotp \text{If } \overline{\npair{(c_{\mathrm{import}},c_{\mathrm{import}})}} \in \lrv(\purePart{W'})\\
      \text{then } \overline{\npair{(c_{\mathrm{export}},c_{\mathrm{export}})}} \in \lrv(\purePart{W'})
  \end{multlined}
    \right\}\\
  &\cup \left\{
    \begin{multlined}
     \npair{(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}),(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})} \;\mid \;\\
     \npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W) \tand\\
      \var{comp} = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss) \tand \\
     \{(c_{\mathrm{main},c}, c_{\mathrm{main},c}),(c_{\mathrm{main},d}, c_{\mathrm{main},d})\} \subseteq (\overline{c_{\mathrm{export}}},\overline{c_{\mathrm{export}}})
       \end{multlined}
    \right\} 
\end{align*}
